---
title: "SENG_533_analysis"
output: html_document
date: "2025-04-23"
---

Lets start analyzing.

```{r, echo=FALSE, message=FALSE}
# Use Libraries
library(ggplot2)

library(GGally)
library(tidyverse)

# Some fancy plotting
library(grDevices)
library(maps)
library(dplyr)
```

Load the data, This stuff is the measurement of each request so there's a lot

```{r}
micro_25.df = read.csv("25_users_micro.csv")
micro_50.df = read.csv("50_users_micro.csv")
micro_75.df = read.csv("75_users_micro.csv")
micro_100.df = read.csv("100_users_micro.csv")

micro_25.df$users <- "25"
micro_50.df$users <- "50"
micro_75.df$users <- "75"
micro_100.df$users <- "100"
```

Here's the aggregate data from JMeter

```{r}
agg_25.df = read.csv("AGG_25_users_micro.csv")
agg_50.df = read.csv("AGG_50_users_micro.csv")
agg_75.df = read.csv("AGG_75_users_micro.csv")
agg_100.df = read.csv("AGG_100_users_micro.csv")
```

Lets combine them into a single data frame to compare them easier

```{r}
users = c("25","25","50","50","75","75","100","100")
dfs = list(agg_25.df, agg_50.df, agg_75.df, agg_100.df)
agg.df = bind_rows(dfs)
agg.df$users <- users
agg.df$users <- factor(agg.df$users, levels = c("25", "50", "75", "100"))
agg.df <- subset(agg.df, Label != "TOTAL")
head(agg.df)
str(agg.df)
```


All measured with a half second delay. in a t2.micro instance.

```{r}
str(micro_25.df)
```

```{r}
#str(micro_50.df)
```

```{r}
#str(micro_75.df)
```

```{r}
#str(micro_100.df)
```

Ok now we can start analyzing. but I'll do that later cuz I'm lazy

```{r}
ggplot(all_micro.df, aes(x = users, y = elapsed, fill = users)) +
  geom_boxplot() +
  labs(title = "Boxplot of Response Times per User Load (t2.micro)",
       x = "Number of Users",
       y = "Elapsed Time (ms)") +
  theme_minimal()
```


```{r}
all_micro.df <- bind_rows(micro_25.df, micro_50.df, micro_75.df, micro_100.df)

ggplot(all_micro.df, aes(x = elapsed, fill = users)) +
  geom_density(alpha = 0.4) +
  coord_cartesian(xlim = c(550, 600)) +
  labs(title = "Response Time Distribution by User Load (t2.micro)",
       x = "Elapsed Time (ms)",
       y = "Density") +
  theme_minimal()
```


Whatever lets do some aggregate stuff now

```{r}
ggplot(agg.df, aes(x = users, y = Throughput)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  geom_text(aes(label = round(Throughput, 1)), vjust = -0.5) +
  labs(title = "Throughput by Number of Users on Micro instance",
       x = "Number of Users",
       y = "Throughput (requests/sec)") +
  theme_minimal()
```

Now for medium instances

```{r}
medium_25.df = read.csv("25_users_medium.csv")
medium_50.df = read.csv("50_users_medium.csv")
medium_75.df = read.csv("75_users_medium.csv")
medium_100.df = read.csv("100_users_medium.csv")

medium_25.df$users <- "25"
medium_50.df$users <- "50"
medium_75.df$users <- "75"
medium_100.df$users <- "100"
```

```{r}
all_medium <- bind_rows(medium_25.df, medium_50.df, medium_75.df, medium_100.df)

ggplot(all_medium, aes(x = elapsed, fill = users)) +
  geom_density(alpha = 0.4) +
  coord_cartesian(xlim = c(550, 600)) +
  labs(title = "Response Time Distribution by User Load (t2.medium)",
       x = "Elapsed Time (ms)",
       y = "Density") +
  theme_minimal()
```

```{r}
ggplot(all_medium, aes(x = users, y = elapsed, fill = users)) +
  geom_boxplot() +
  labs(title = "Boxplot of Response Times per User Load (t2.micro)",
       x = "Number of Users",
       y = "Elapsed Time (ms)") +
  theme_minimal()
```

Its pretty localized to that one spot.

Here's the aggregate data from JMeter

```{r}
agg_25medium.df = read.csv("AGG_25_users_medium.csv")
agg_50medium.df = read.csv("AGG_50_users_medium.csv")
agg_75medium.df = read.csv("AGG_75_users_medium.csv")
agg_100medium.df = read.csv("AGG_100_users_medium.csv")
```

Lets combine them into a single data frame to compare them easier

```{r}
users = c("25","25","50","50","75","75","100","100")
dfs = list(agg_25medium.df, agg_50medium.df, agg_75medium.df, agg_100medium.df)
aggmedium.df = bind_rows(dfs)
aggmedium.df$users <- users
aggmedium.df$users <- factor(aggmedium.df$users, levels = c("25", "50", "75", "100"))
aggmedium.df <- subset(aggmedium.df, Label != "TOTAL")
head(aggmedium.df)
str(aggmedium.df)
```

```{r}
ggplot(aggmedium.df, aes(x = users, y = Throughput)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  geom_text(aes(label = round(Throughput, 1)), vjust = -0.5) +
  labs(title = "Throughput by Number of Users on medium instance",
       x = "Number of Users",
       y = "Throughput (requests/sec)") +
  theme_minimal()
```

combine them for more analysis

```{r}
agg.df$instance <- "micro"
aggmedium.df$instance <- "medium"

agg_all.df <- bind_rows(agg.df, aggmedium.df)
```

Another plot

```{r}
ggplot(agg_all.df, aes(x = users, y = Throughput, fill = instance)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(Throughput, 1)), 
            position = position_dodge(width = 0.9), vjust = -0.5) +
  labs(title = "Throughput Comparison: Micro vs Medium EC2 Instances",
       x = "Number of Users",
       y = "Throughput (requests/sec)") +
  theme_minimal()
```

